---
title: "EstuarineFishGillMicrobiota_part1_21.07.24"
output: html_document
date: "2024-07-21"
---

Hand over from dada2 output to phyloseq followed by abundance filtering in the individual datasets
Chapter 13 and 14 include visualizations of abiotic and stable isotope data. 

# 1 Global Setup 

## 1.1 Path

before you start: 
.rs.restartR()

```{r,  message=FALSE, warning=FALSE, include=FALSE}
GitClonePath <- "/Users/admin/Desktop/EstuarineFishGillMicrobiota"
setwd(GitClonePath)

path_Input_16S <- paste(GitClonePath, "Fish_Input_16S", sep="/")

#Output of the individual Pipeline parts including .rds and .csv
path_Output_16S <- paste(GitClonePath, "Fish_Output_16S", sep="/")

#Output of all plots, the markdowns include only selections
pathPlots          <- paste(GitClonePath, "Fish_Plots", sep="/")

#Create Folder if not existing
ifelse(!dir.exists(file.path(GitClonePath, "Fish_Output_16S")), dir.create(file.path(GitClonePath, "Fish_Output_16S")), FALSE)
ifelse(!dir.exists(file.path(GitClonePath, "Fish_Plots")), dir.create(file.path(GitClonePath, "Fish_Plots")), FALSE)

```

## 1.2 Packages

```{r}
# R package management tools such as packrat or renv. These tools allow you to create isolated environments with specific versions of R and installed packages, ensuring reproducibility and avoiding conflicts with other packages installed in your system.
#install.packages("packrat")
#packrat::init()
#packrat::snapshot()
#packrat::restore()

# if (!require("BiocManager", quietly = TRUE))
#     install.packages("BiocManager")
# BiocManager::install(c(
#   "DESeq2",
#   "ComplexHeatmap",
#   "Biostrings",
#   "BiocParallel",
#   "BiocNeighbors",
#   "BiocFileCache",
#   "BiocBaseUtils",
#   "ShortRead",
#   "SummarizedExperiment",
#   "TreeSummarizedExperiment",
#   "phyloseq",
#   "tidyverse",
#   "plyr",
#   "dplyr",
#   "cowplot",
#   "ggrepel",
#   "PCAtools",
#   "ComplexHeatmap",
#   "WGCNA",
#   "dada2",
#   "ShortRead",
#   "phyloseq",
#   "factoextra",
#   "microbiome", #clr transformation
#   "mia",
#   ), force =T)

#install.packages("remotes")
#remotes::install_github("jfq3/ggordiplots")
#install.packages("devtools")
#install.packages("ggordiplots")
#install.packages("RcmdrMisc")
#install.packages("adespatial")
#install.packages("ggVennDiagram")
#install.packages("ggpicrust2")
```

## 1.3 Functions

```{r,  message=FALSE, warning=FALSE, include=FALSE}
#Source the Fish_Functions_19.07.24_Paper.Rmd placed in the working directory
#noamross/source_rmd.R
#https://gist.github.com/noamross/a549ee50e8a4fd68b8b1
source_rmd = function(file, skip_plots = TRUE) {
  temp = tempfile(fileext=".R")
  knitr::purl(file, output=temp)

  if(skip_plots) {
    old_dev = getOption('device')
    options(device = function(...) {
      .Call("R_GD_nullDevice", PACKAGE = "grDevices")
    })
  }
  source(temp)
  if(skip_plots) {
    options(device = old_dev)
  }
}
source_rmd("Fish_Functions_19.07.24_Paper.Rmd")
```



## 1.4 Input Files

```{r, message=FALSE, warning=FALSE}
#Sequencing was performed in 3 runs and 2 batches, Batch1 was sequenced twice to increase sequencing depth
#all runs were individually processed in the Dada2 pipeline and merged at the seqtab step
#########################
#Read DADA2 Output files#

taxa  <-readRDS(file.path(path_Input_16S, "Fish_17.09.23_mergemerge-Taxa_Species.rds"))
seqtab.nochim <-  readRDS(file.path(path_Input_16S, "Fish_17.09.23_mergeseqtab.nochim.rds"))
ReadNum1 <-  read.csv2(file.path(path_Input_16S, "Fish_Batch1-31.07.23_470_Track_reads_through_pipeline.csv"))
ReadNum2 <-  read.csv2(file.path(path_Input_16S, "Fish_Batch1-Reseq-31.07.23_470_Track_reads_through_pipeline.csv"))
ReadNum3 <-  read.csv2(file.path(path_Input_16S, "Fish_Batch2-26.07.23_470_Track_reads_through_pipeline.csv"))

########################################################################
#Import samplefile and filter for samples with successful 16S sequencing
library(readxl)
SAMDF16S<- as.data.frame(read_excel(file.path(path_Input_16S, "Fish_samplefile_24.03.2024.xlsx")))[,-1]
write.table(SAMDF16S, file=file.path(path_Input_16S, "Fish_samplefile_24.03.2024.csv"), sep=";",dec = ".")

SAMDF16S <-read.table(file=file.path(path_Input_16S, "Fish_samplefile_24.03.2024.csv"), sep=";",dec = ".")
rownames(SAMDF16S) <- SAMDF16S$SampleID

```


## 1.5 Tutorials

```{r, message=FALSE, warning=FALSE,  include=FALSE}
#https://userweb.eng.gla.ac.uk/umer.ijaz/projects/microbiomeSeq_Tutorial.html#co-occur

#NEW Works on summarized Expderiments
#https://microbiome.github.io/OMA/differential-abundance.html#differential-abundance-analysis

#Bioconductor by Callahan
#https://bioconductor.org/help/course-materials/2017/BioC2017/Day1/Workshops/Microbiome/MicrobiomeWorkflowII.html#hierarchical_multiple_testing

#Microbiome seq
#https://userweb.eng.gla.ac.uk/umer.ijaz/projects/microbiomeSeq_Tutorial.html
#https://userweb.eng.gla.ac.uk/umer.ijaz/bioinformatics/ecological.html

#Olberding
#https://www.nicholas-ollberding.com/post/introduction-to-the-statistical-analysis-of-microbiome-data-in-r/

#Nice DESEQ2
#https://astrobiomike.github.io/amplicon/dada2_workflow_ex

#CAP Plot
#https://deneflab.github.io/MicrobeMiseq/demos/mothur_2_phyloseq.html
```


## 1.6 Setup Analysis

```{r, message=FALSE, warning=FALSE}
#Date of the Analysis for save-names#
Date <- "19.07.2024"
set.seed(123)
Species    <- "OE_GC"
Kind       <- "Fish"
Tissue     <- "Gill"
Year       <- "2021_2022"
Season     <- "SU_AU_WI_SP"
Type       <- "16S"
alpha      <- 0.05
OperatingSystem <- "Windows"
prefix <- "SSU-"
#Differential Abundance Testing
OutlineColor <- "grey20"

#####################
variable = Comparisons = "Replicates2"
#####################
LocOrder=c("Medem Grund", "Brunsbuettel", "Schwarztonnen Sand", "Twielenfleth","Muehlenberger Loch")
SeasonOrder <-c("Summer_21", "Autumn_21", "Winter_22", "Spring_22")
CruiseOrder<-c("Elbe_Summer_21", "Elbe_Autumn_21", "Elbe_Winter_22","Elbe_Spring_22")

VariableOrder<-c(
  "GCSU21BB", "GCSU21SS", "GCSU21TW", "GCSU21ML", 
  "GCAU21BB", "GCAU21SS", "GCAU21TW", "GCAU21ML", 
  "GCWI22BB", "GCWI22SS",             "GCWI22ML", 
  "GCSP22BB", "GCSP22SS", "GCSP22TW", "GCSP22ML", 
  
  "OESU21MG", "OESU21BB", "OESU21SS", "OESU21TW", "OESU21ML", 
  "OEAU21MG", "OEAU21BB", "OEAU21SS", "OEAU21TW", "OEAU21ML",
  "OEWI22MG", "OEWI22BB", "OEWI22SS", "OEWI22TW", "OEWI22ML",
  "OESP22MG", "OESP22BB", "OESP22SS", "OESP22TW", "OESP22ML",
  
  "WF")


LocOrder=c("Medem Grund", "Brunsbuettel", "Schwarztonnen Sand","Twielenfleth", "Muehlenberger Loch")
LOCOrder=c("MG-713", "BB-692", "SS-665","TF-651", "ML-633")
save_name <- paste(Species,Year,Season,sep = "_")
#Check your Output: 
paste0(file.path(path_Output_16S, "DAT_"), save_name, ".RData")

SAMDF16S$LOC<-ifelse(SAMDF16S$Loc == "Medem Grund", "MG-713",
                      ifelse(SAMDF16S$Loc == "Brunsbuettel", "BB-692",
                          ifelse(SAMDF16S$Loc == "Schwarztonnen Sand", "SS-665",
                                  ifelse(SAMDF16S$Loc == "Twielenfleth", "TF-651",
                                        ifelse(SAMDF16S$Loc == "Muehlenberger Loch", "ML-633", NA)))))

SAMDF16S$"geographic.location..latitude."<-ifelse(SAMDF16S$Loc == "Medem Grund", "53.8363",
                      ifelse(SAMDF16S$Loc == "Brunsbuettel", "53.8874",
                          ifelse(SAMDF16S$Loc == "Schwarztonnen Sand", "53.71442",
                                  ifelse(SAMDF16S$Loc == "Twielenfleth", "53.60921",
                                        ifelse(SAMDF16S$Loc == "Muehlenberger Loch", "53.54907", NA)))))
SAMDF16S$"geographic.location..longitude."<-ifelse(SAMDF16S$Loc == "Medem Grund", "8.88777",
                      ifelse(SAMDF16S$Loc == "Brunsbuettel", "9.19429",
                          ifelse(SAMDF16S$Loc == "Schwarztonnen Sand", "9.46976",
                                  ifelse(SAMDF16S$Loc == "Twielenfleth", "9.56536",
                                        ifelse(SAMDF16S$Loc == "Muehlenberger Loch", "9.82338", NA)))))

SAMDF16S$Reps <- sub("^.{2}", "", SAMDF16S$Replicates2)
SAMDF16S$Reps<- ifelse(SAMDF16S$Reps == "SU21MG", "SU 713",
                            ifelse(SAMDF16S$Reps == "SU21BB", "SU 692",
                            ifelse(SAMDF16S$Reps == "SU21SS", "SU 665",
                            ifelse(SAMDF16S$Reps == "SU21TW", "SU 651",
                            ifelse(SAMDF16S$Reps == "SU21ML", "SU 633", 
                                   
                            ifelse(SAMDF16S$Reps == "AU21MG", "AU 713",
                            ifelse(SAMDF16S$Reps == "AU21BB", "AU 692",
                            ifelse(SAMDF16S$Reps == "AU21SS", "AU 665",
                            ifelse(SAMDF16S$Reps == "AU21TW", "AU 651",
                            ifelse(SAMDF16S$Reps == "AU21ML", "AU 633", 
                            
                            ifelse(SAMDF16S$Reps == "WI22MG", "WI 713",
                            ifelse(SAMDF16S$Reps == "WI22BB", "WI 692",
                            ifelse(SAMDF16S$Reps == "WI22SS", "WI 665",
                            ifelse(SAMDF16S$Reps == "WI22TW", "WI 651",
                            ifelse(SAMDF16S$Reps == "WI22ML", "WI 633", 
                                   
                            ifelse(SAMDF16S$Reps == "SP22MG", "SP 713",
                            ifelse(SAMDF16S$Reps == "SP22BB", "SP 692",
                            ifelse(SAMDF16S$Reps == "SP22SS", "SP 665",
                            ifelse(SAMDF16S$Reps == "SP22TW", "SP 651",
                            ifelse(SAMDF16S$Reps == "SP22ML", "SP 633", 
                                   "WF")))))
                            )))))))))))))))

     RepOrder <-c(
    "SU 713", "SU 692","SU 665","SU 651","SU 633", 
    "AU 713","AU 692","AU 665","AU 651","AU 633", 
    "WI 713","WI 692","WI 665","WI 651","WI 633", 
    "SP 713","SP 692","SP 665","SP 651","SP 633")
     

SAMDF16S$RepsSpecs <- paste(SAMDF16S$Species, SAMDF16S$Reps, sep=" ")
SAMDF16S$RepsSpecs[SAMDF16S$RepsSpecs == "WF"] <- "WF"

SAMDF16S$HSI     <- SAMDF16S$LiverWeight/SAMDF16S$Weight*100
SAMDF16S$SSI     <- SAMDF16S$SpleenWeight/SAMDF16S$Weight*100
SAMDF16S$GSI     <- SAMDF16S$GonadWeight/SAMDF16S$Weight*100
SAMDF16S$FCF <-  (100*SAMDF16S$Weight/(SAMDF16S$Length/10)^3)
SAMDF16S$FI  <- SAMDF16S$StomachContent/SAMDF16S$Weight*100
 
SAMDF16S <- SAMDF16S %>% mutate(Maturity = case_when(
                    (Species== "GC" & Length >= 10.5) ~ "Adult", 
                    (Species== "GC" & Length < 10.5) ~ "Juvenile", 
                    (Species== "OE" & Length >= 10) ~ "Adult", Length < 10 ~ "Juvenile"))

SAMDF16S <- SAMDF16S %>% 
  mutate(Age = case_when(
    Species != "OE" ~ as.character(Age),  
    (Species == "OE" & Length < 90) ~ "0", 
    (Species == "OE" & Length <= 130) ~ "1", 
    (Species == "OE" & Length <= 180) ~ "2", 
    (Species == "OE" & Length <= 220) ~ "3", 
    (Species == "OE" & Length > 220) ~ "4"
  ))
SAMDF16S$Age <- as.numeric(SAMDF16S$Age)

SAMDF16S$fSeason <- factor(SAMDF16S$Season, level = SeasonOrder)
SAMDF16S$fLOC <- factor(SAMDF16S$LOC, level = LOCOrder)
SAMDF16S$Species <- substr(SAMDF16S$SampleID, 1, nchar(SAMDF16S$SampleID) - 9)
SAMDF16S$fReplicates <- factor(SAMDF16S$Replicates, levels = VariableOrder[VariableOrder %in%                                                                               SAMDF16S$Replicates])

SAMDF16S$fCruise <- factor(SAMDF16S$Cruise, level = CruiseOrder)

#Adding in Elbe Estuary Public Monitoring Data from https://www.fgg-elbe.de/fachinformationssystem.html
Mean_AbioticsFGG <- readRDS(file.path(path_Input_16S, "Mean_AbioticsFGG_16.02.24.rds"))
names(Mean_AbioticsFGG)[names(Mean_AbioticsFGG) == "Season"] <- "Cruise"
names(SAMDF16S)[names(SAMDF16S) == "O2"] <- "O2_catch"
names(SAMDF16S)[names(SAMDF16S) == "O2Sat"] <- "O2Sat_catch"
names(SAMDF16S)[names(SAMDF16S) == "pH"] <- "pH_catch"

colnames(Mean_AbioticsFGG) <- sub("_mean", "",colnames(Mean_AbioticsFGG))
SAMDF16S <- dplyr::left_join(SAMDF16S, Mean_AbioticsFGG)

SSU_Samples <-c(
#Ruffe
#Summer21
"GCSU21BBEB1", "GCSU21BBEB2", "GCSU21BBEB4", "GCSU21BBEB5",                              "GCSU21BBFL3",
"GCSU21SSEB1", "GCSU21SSEB2", "GCSU21SSEB3", "GCSU21SSEB4", "GCSU21SSEB8","GCSU21SSFL1", "GCSU21SSFL3",
"GCSU21TWEB1", "GCSU21TWEB2", "GCSU21TWEB3", "GCSU21TWEB4", "GCSU21TWFL1", "GCSU21TWFL2", "GCSU21TWFL3",
"GCSU21MLEB1", "GCSU21MLEB2", "GCSU21MLEB3", "GCSU21MLEB5", "GCSU21MLEB6", "GCSU21MLFL1", "GCSU21MLFL2", "GCSU21MLFL3", "GCSU21MLFL6",

#"GCSU21BBEB6" missing physiology
#"GCSU21BBFL2" equal to water samples 

#Autumn21
"GCAU21BBEB1", "GCAU21BBEB2", "GCAU21BBEB3", "GCAU21BBFL1", "GCAU21BBFL2", "GCAU21BBFL3", "GCAU21BBFL4",
"GCAU21SSEB1", "GCAU21SSEB3", "GCAU21SSEB5", "GCAU21SSEB7", "GCAU21SSFL1", "GCAU21SSFL3", "GCAU21SSFL5",
"GCAU21TWEB1", "GCAU21TWFL1", "GCAU21TWFL2",
"GCAU21MLEB1", "GCAU21MLEB2", "GCAU21MLEB3", "GCAU21MLFL1", "GCAU21MLFL3", "GCAU21MLFL5", "GCAU21MLFL7", 
#Winter21
"GCWI22BBEB1", "GCWI22BBFL1", "GCWI22BBFL2",
"GCWI22SSEB1", "GCWI22SSEB2", "GCWI22SSEB3", "GCWI22SSFL1", "GCWI22SSFL2", 
"GCWI22MLEB1", "GCWI22MLFL1", "GCWI22MLFL2",
#Spring21
"GCSP22BBEB1", "GCSP22BBEB3", "GCSP22BBEB5", "GCSP22BBEB7", "GCSP22BBEB9", "GCSP22BBFL1", "GCSP22BBFL2",
"GCSP22SSEB1", "GCSP22SSEB3", "GCSP22SSEB5", "GCSP22SSEB7", "GCSP22SSFL1", "GCSP22SSFL3", "GCSP22SSFL5",
"GCSP22TWEB1", "GCSP22TWFL1", "GCSP22TWFL2", "GCSP22TWFL3",   
"GCSP22MLEB1", "GCSP22MLEB3", "GCSP22MLEB5", "GCSP22MLEB7", "GCSP22MLFL1", "GCSP22MLFL3", "GCSP22MLFL5",
#Summer22 ML
#"GCSU22MLEB1", "GCSU22MLEB2", "GCSU22MLEB3", "GCSU22MLEB4", "GCSU22MLEB5", "GCSU22MLEB6", "GCSU22MLEB7",  

#Smelt
"OESU21MGEB1", "OESU21MGEB4", "OESU21MGEB6", "OESU21MGEB8", "OESU21MGEB9", "OESU21MGFL2", "OESU21MGFL6",
"OESU21BBEB5", "OESU21BBEB6", "OESU21BBEB7", "OESU21BBEB8", "OESU21BBEB9", "OESU21BBFL1", "OESU21BBFL4",
"OESU21SSEB6", "OESU21SSEB7", "OESU21SSEB8", "OESU21SSEB9", "OESU21SSFL1", "OESU21SSFL2", "OESU21SSFL6",
"OESU21TWEB2", "OESU21TWEB3", "OESU21TWEB4", "OESU21TWFL1", "OESU21TWFL3", "OESU21TWFL5", "OESU21TWFL7",
"OESU21MLEB1", "OESU21MLEB2", "OESU21MLEB3", "OESU21MLFL1", "OESU21MLFL2",

"OEAU21MGEB1", "OEAU21MGEB3", "OEAU21MGEB5", "OEAU21MGEB7", "OEAU21MGFL1", "OEAU21MGFL3", "OEAU21MGFL5",
"OEAU21BBEB1", "OEAU21BBEB3", "OEAU21BBEB6", "OEAU21BBEB7", "OEAU21BBFL2", "OEAU21BBFL4", "OEAU21BBFL6",
"OEAU21SSEB1", "OEAU21SSEB3", "OEAU21SSEB5", "OEAU21SSEB8", "OEAU21SSFL1", "OEAU21SSFL3", "OEAU21SSFL6",
"OEAU21TWEB1", "OEAU21TWEB3", "OEAU21TWEB5", "OEAU21TWEB7", "OEAU21TWFL1", "OEAU21TWFL3", "OEAU21TWFL7",
"OEAU21MLEB1", "OEAU21MLEB3", "OEAU21MLEB5", "OEAU21MLEB7", "OEAU21MLFL1", "OEAU21MLFL3", "OEAU21MLFL7",

"OEWI22BBEB1", "OEWI22BBEB4", "OEWI22BBEB5", "OEWI22BBEB7", "OEWI22BBFL1", "OEWI22BBFL3", "OEWI22BBFL7", 
"OEWI22MGEB1", "OEWI22MGEB3", "OEWI22MGEB5", "OEWI22MGEB9", "OEWI22MGFL1", "OEWI22MGFL3", "OEWI22MGFL7",
"OEWI22SSEB1", "OEWI22SSEB5", "OEWI22SSEB7", "OEWI22SSEB9", "OEWI22SSFL1", "OEWI22SSFL5", "OEWI22SSFL8",  
"OEWI22TWEB1", "OEWI22TWEB2", "OEWI22TWEB3", "OEWI22TWEB4", "OEWI22TWEB5", "OEWI22TWEB7", "OEWI22TWEB9",
"OEWI22MLEB1", "OEWI22MLEB3", "OEWI22MLEB7", "OEWI22MLEB9", "OEWI22MLFL1", "OEWI22MLFL5", "OEWI22MLFL7", 

"OESP22MGEB1", "OESP22MGEB3", "OESP22MGEB5", "OESP22MGEB7", "OESP22MGFL1", "OESP22MGFL3", "OESP22MGFL5",
"OESP22BBEB1", "OESP22BBEB3", "OESP22BBEB7", "OESP22BBEB8", "OESP22BBFL2", "OESP22BBFL3", "OESP22BBFL5",
"OESP22SSEB1", "OESP22SSEB2", "OESP22SSEB3", "OESP22SSEB4", "OESP22SSFL1", "OESP22SSFL3", "OESP22SSFL5",
"OESP22TWEB1", "OESP22TWEB2", "OESP22TWEB5", "OESP22TWFL1", "OESP22TWFL3", "OESP22TWFL5", "OESP22TWFL7",
"OESP22MLEB1", "OESP22MLEB2", "OESP22MLEB3", "OESP22MLFL1", "OESP22MLFL2", "OESP22MLFL3", "OESP22MLFL4",

#"OESU22MLEB1", "OESU22MLEB2", "OESU22MLEB3", "OESU22MLEB4", 

"WFSU21MGEB",
"WFSU21BBEB",
"WFSU21SSFL",
"WFSU21MLFL", 

"WFAU21TWEB",

"WFWI22MGEB", "WFWI22MGFL",
"WFWI22BBEB", "WFWI22BBFL",
"WFWI22MLFL", "WFWI22SSFL", 

"WFSP22MGEB", "WFSP22MGFL",
"WFSP22BBEB", "WFSP22BBFL", 
"WFSP22SSEB", "WFSP22SSFL",
"WFSP22MLEB", "WFSP22MLFL"

#"WFSU22MLEB"
)
      
SAMDF16S$Species[SAMDF16S$Species == "W"] <- "WF"
SAMDF16S$fSpecies <- factor(SAMDF16S$Species, levels=c("WF", "OE", "GC"))


###########################################################################################################
#For ENA_Sample Submission! Open in Numbers or Libre office, stupid Excel will destroy geo and other data!#
###########################################################################################################
  write.table(SAMDF16S, paste0(file.path(path_Output_16S, paste(paste(save_name,
            paste("SAMDF16S", sep=""),sep="_"),".txt", sep=""))), dec = ".", sep = "\t")
```


#-

# 2 Phyloseq

hand over from dada2 to phyloseq to store data

```{r, message=FALSE, warning=FALSE}
#Create a phyloseq object from Dada2 Output
library(tidyverse)
taxa  <-readRDS(file.path(path_Input_16S, "Fish_17.09.23_mergemerge-Taxa_Species.rds"))
seqtab.nochim <-  readRDS(file.path(path_Input_16S, "Fish_17.09.23_mergeseqtab.nochim.rds"))

taxa<-as.matrix(taxa)
library(phyloseq)
ps <- phyloseq(otu_table(seqtab.nochim, taxa_are_rows=FALSE), tax_table(taxa))

dna <- Biostrings::DNAStringSet(taxa_names(ps))
names(dna) <- taxa_names(ps)
ps <- merge_phyloseq(ps, dna)
taxa_names(ps) <- paste0("ASV", seq(ntaxa(ps)))
ps

ReadNum1 <-  read.csv2(file.path(path_Input_16S, "Fish_Batch1-31.07.23_470_Track_reads_through_pipeline.csv"))
ReadNum2 <-  read.csv2(file.path(path_Input_16S, "Fish_Batch1-Reseq-31.07.23_470_Track_reads_through_pipeline.csv"))
ReadNum3 <-  read.csv2(file.path(path_Input_16S, "Fish_Batch2-26.07.23_470_Track_reads_through_pipeline.csv"))

ReadNum <- rbind(ReadNum1, ReadNum2, ReadNum3)
ReadNum<-ReadNum[,c("X", "input")]
colnames(ReadNum)<-c("SampleID", "Input")
ReadNum <- ReadNum %>%
  dplyr::group_by(SampleID) %>%
  dplyr::summarise(Input = sum(Input))

nonchim <- as.data.frame(rowSums(otu_table(ps)))
names(nonchim) <- "nonchim"
ReadNum<- dplyr::left_join(rownames_to_column(nonchim), ReadNum, by=c("rowname" = "SampleID"))
colnames(ReadNum)<-c("SampleID", "nonchim", "Input")
rownames(ReadNum) <- ReadNum$SampleID

OTU <- otu_table(ps)
TAX <- tax_table(ps) 
REFSEQ <- refseq(ps)

ps <- phyloseq(otu_table(OTU, taxa_are_rows=FALSE), 
               sample_data(ReadNum), tax_table(TAX), refseq(REFSEQ))

head(sample_names(ps))
head(rowSums(otu_table(ps)))
sample_names(ps)[sample_names(ps) == "Elbe915"] <- "WFSU21MGEB"
sample_names(ps)[sample_names(ps) == "Elbe917"] <- "WFSU21BBEB"
sample_names(ps)[sample_names(ps) == "WFAUT21TWEB"] <- "WFAU21TWEB"

head(rowSums(otu_table(ps)))


###########
#Save Data#
###########
ps <- prune_samples(sample_names(ps) %in% SSU_Samples, ps)
ps <- microViz::ps_reorder(ps, SSU_Samples)

saveRDS(ps, file.path(path_Output_16S, paste(paste("Fish_ps_16S_merge", Date, sep="_"), "rds", sep=".")))
ps <- readRDS(file.path(path_Output_16S, paste(paste("Fish_ps_16S_merge", Date, sep="_"), "rds", sep=".")))

```

# 3 Filter ASVs 

Filtering ASVs for 0.005% relative abundance per dataset excluding rare taxa reducing risks of spurious correlations in the later analyses 


```{r, message=FALSE, warning=FALSE}
#https://github.com/joey711/phyloseq/issues/574
require(phyloseq)
require(dada2)
require(tidyverse)
head(as.data.frame(rowSums(otu_table(ps))))

pslistraw <- list("ps" = ps)
for (i in names(pslistraw)[grepl("ps", names(pslistraw))]){
    ps <- pslistraw[[i]]
    g <- names(pslistraw[i])
    A = data.frame(sample_data(ps))
    A<-A %>% mutate(Run =case_when(
    A$SampleID %in% c(ReadNum2$X) ~ "Batch1_Run1merge",
    A$SampleID %in% c(ReadNum3$X) ~ "Batch2"))
    #PHY <-phy_tree(ps)
    OTU <- otu_table(ps, taxa_are_rows=FALSE)
    TAX <- tax_table(ps)
    REFSEQ <- refseq(ps)
    pslistraw[[i]] <- phyloseq(otu_table(OTU, taxa_are_rows=FALSE), 
               sample_data(A), tax_table(TAX), refseq(REFSEQ)) #, phy_tree(PHY)
}

####################################################################
#Creat differently splitted datasets to answer individual questions#
ps_SSU <-prune_samples(sample_names(pslistraw$ps)[grepl("GC|OE|WF", sample_names(pslistraw$ps))], pslistraw$ps)
ps_WF <-prune_samples(sample_names(pslistraw$ps)[grepl("WFSU|WFAU|WFSP|WFWI", sample_names(pslistraw$ps))], pslistraw$ps)
ps_Fish <-prune_samples(sample_names(pslistraw$ps)[grepl("GC|OE", sample_names(pslistraw$ps))], pslistraw$ps)
ps_OE <-prune_samples(sample_names(ps_Fish)[grepl("OE", sample_names(ps_Fish))], ps_Fish)
ps_GC <-prune_samples(sample_names(ps_Fish)[grepl("GC", sample_names(ps_Fish))], ps_Fish)

ps_OEWF <-prune_samples(sample_names(ps_SSU)[grepl("WFSU|WFAU|WFSP|WFWI|OE", sample_names(ps_SSU))], ps_SSU)
ps_GCWF <-prune_samples(sample_names(ps_SSU)[grepl("WFSU|WFAU|WFSP|WFWI|GC", sample_names(ps_SSU))], ps_SSU)

pslistraw<- list("ps_SSU" = ps_SSU, "ps_WF" = ps_WF, "ps_Fish" = ps_Fish, "ps_OE" = ps_OE, "ps_GC" = ps_GC, "ps_OEWF" = ps_OEWF, "ps_GCWF" =ps_GCWF)

###########
#Save Data#
###########
saveRDS(pslistraw, file.path(path_Output_16S, paste(paste(save_name,"ps_16S_merge_pslistraw", Date, sep="_"), ".rds", sep="")))

#########################
#Adding real sample data#
#########################
for (i in names(pslistraw)[grepl("ps", names(pslistraw))]){
    ps_SAMDF <- pslistraw[[i]]
    g<- i; print(g)

    A<-SAMDF16S[SAMDF16S$SampleID %in% rownames(sample_data(ps_SAMDF)),]
    B <-dplyr::left_join(A, sample_data(ps_SAMDF))
    rownames(B) <- B$SampleID
    B <-phyloseq::sample_data(B)

    #PHY <-phy_tree(ps)
    OTU <- phyloseq::otu_table(ps_SAMDF, taxa_are_rows=FALSE)
    TAX <- phyloseq::tax_table(ps_SAMDF)
    REFSEQ <- refseq(ps_SAMDF)
    pslistraw[[i]] <- phyloseq(OTU, TAX, B, REFSEQ) #, phy_tree(PHY)
}

##############################################################################
#Filtering threshold determined to reduce sparsity but keep overall abundance#
applied_filter <- 0.005
print(paste("The Filtering Abundance is", applied_filter, "%"))
 
for (i in names(pslistraw)[grepl("ps", names(pslistraw))]) {
    require(cowplot)
    require(phyloseq)
    require(ggplot2)
    tryCatch({
    ps <- pslistraw[[i]]
    g<- names(pslistraw[i])
    ###### Pre-Filtering Step 1: Remove all not bacteria
    table(tax_table(ps)[, "Phylum"], exclude = NULL)
    ps_Filter <- ps %>%
    prune_taxa(taxa_sums(.) > 0, .) # prune OTUs that are not present in at least one sample
    ps_Filter1 <- ps_Filter %>% #Filter everything that is not bacteria
    subset_taxa(
    Kingdom == "Bacteria" &
    Family  != "mitochondria" &
    Class   != "Chloroplast")

    if (g %in% c("ps_SSU")) {
      A<-as.data.frame(rowSums(otu_table(ps)))
      B<-as.data.frame(rowSums(otu_table(ps_Filter1)))
      BB <- (B - A)/A*100
      print("We loose reads by Chloroplast & Mitochondria removal")
      print(BB)
    }
 
    ###### Pre-Filtering Step 2: Remove all uncharacterized
    ps_Filter2 <- subset_taxa(ps_Filter1, !is.na(Phylum) & !Phylum %in% c("", "uncharacterized"))
    
    #table(tax_table(ps_Filter2)[, "Phylum"], exclude = NULL)

    ###### Pre-Filtering Step 3: Glom to species level
    #ps_Filter_glom = tax_glom(ps_Filter2, "Species", NArm = FALSE) 
    #head(tax_table(ps_Filter_glom))
    #following http://mixomics.org/mixmc/mixmc-preprocessing/
    #Arumugam et al., (2011)

    
    low.count.removal <- function(
                        data, # OTU count df of size n (sample) x p (OTU)
                        percent=0.005 # cutoff chosen
                        ) {
    keep.otu = which(colSums(data)*100/(sum(colSums(data))) > percent)
    data.filter = data[,keep.otu]
    return(list(data.filter = data.filter, keep.otu = keep.otu))}

    #######################################################
    #Plot consequence of filtering from Strand et al, 2021#
    #######################################################
    frac_zero <- c()
    all_sum   <- c()
    num_otu   <- c()
    seqp <- seq(0,0.1,0.0001)
    for(i in seqp){
      result.filter = low.count.removal(otu_table(ps_Filter2), percent=i)
      length(result.filter$keep.otu)
      otu.f = result.filter$data.filter
      frac_zero <- c(frac_zero, sum(otu.f == 00)/ (ncol(otu.f)*nrow(otu.f)))
      all_sum <- c(all_sum, sum(otu.f))
      num_otu <- c(num_otu, ncol(otu.f))
    }
    names(frac_zero) <- seqp
    names(all_sum) <- seqp

    # Get all_sum and num_otu to a fraction of the total
    mas <- max(all_sum)
    mno <- max(num_otu)

    all_sum %>% (function(x){x/max(x)}) -> all_sum
    num_otu %>% (function(x){x/max(x)}) -> num_otu
    data.frame(filter = seqp, 
           Percent.zeros   = frac_zero*100, 
           Total.abundance = all_sum*100, 
           Number.of.OTUs  = num_otu*100) %>% 
    tidyr::gather(key = "Type", value = "percent.of.total", -filter) %>%
    ggplot() + 
    geom_line(mapping = aes(x = filter, y = percent.of.total, col = Type)) +
    geom_vline(xintercept = applied_filter, alpha = 0.5, color = "red", linetype="dashed")+
    ylab("Percent of total") +
    xlab(paste("Filter at", applied_filter)) +
    theme(legend.title = element_blank()) -> FilterZerosPlot

    plot(FilterZerosPlot)
    
    ggsave(FilterZerosPlot, filename = paste(paste(save_name,"FilterZerosPlot", i, sep="_"), 
                                           ".png", sep=""), 
             path = pathPlots , device='png', dpi=300, width = 7, height = 5)
      
    ########################
    # remove low count OTUs#
    ########################
    result.filter <- low.count.removal(otu_table(ps_Filter2), percent=applied_filter) 
    data.filter <- result.filter$data.filter
    length(result.filter$keep.otu) # check how many OTUs remain

    ps_Filter3 <- prune_taxa(names(result.filter$keep.otu), ps_Filter2)

    #tail(t(otu_table(ps_Filter3)))
    #table(rowSums(t(otu_table(ps_Filter3))))

    ###### Pre-Filtering Step 4: Add best taxonomy to ASV
    ps_Filter_ASV_besttax<- add_besthit(ps_Filter3, sep=":")

    ###### Excluding samples with low sequencing depth
    #Check sample depths
    #print(sample_sums(ps_Filter))
    #print(sample_sums(ps_Filter_ASV_besttax))

    ###### Pre-Filtering Step 5: Remove low frequency Samples
    print(paste("Samples removed for low frequency below 1000 seqs in;", g, sep = ""))
    print(which(!rowSums(otu_table(ps_Filter_ASV_besttax)) > 1000))

    
    head(rowSums(otu_table(ps_Filter_ASV_besttax)))
    library(phyloseq)
    ps_Filter_ASV_besttax_Samples <- prune_samples(rowSums(otu_table(ps_Filter_ASV_besttax)) > 1000,
                                                            ps_Filter_ASV_besttax) 
    
    ps_Filter_ASV_besttax_Samples <- ps_Filter_ASV_besttax_Samples %>% prune_taxa(taxa_sums(.) > 0, .) 
    #ps_Filter_ASV_besttax_Samples <- filter_taxa(ps_Filter_ASV_besttax_Samples, function (x) {sum(x > 0) > 1},
    #                                 prune=TRUE) 
    saveRDS(ps_Filter_ASV_besttax_Samples, file.path(path_Output_16S,paste(g, paste(paste("Filter_ASV_besttax_16S", Date, sep="_"), ".rds", sep=""), sep="_")))
    }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
  }
  
#####################################################
#Creating a dynamic list object that we loop through#
ps_SSU      <- readRDS(file.path(path_Output_16S, paste("ps_SSU", paste(paste("Filter_ASV_besttax_16S", Date, sep="_"), ".rds", sep=""), sep="_")))
ps_WF      <- readRDS(file.path(path_Output_16S, paste("ps_WF", paste(paste("Filter_ASV_besttax_16S", Date, sep="_"), ".rds", sep=""), sep="_")))
ps_Fish   <- readRDS(file.path(path_Output_16S, paste("ps_Fish", paste(paste("Filter_ASV_besttax_16S", Date, sep="_"), ".rds", sep=""), sep="_")))
ps_OE <- readRDS(file.path(path_Output_16S, paste("ps_OE", paste(paste("Filter_ASV_besttax_16S", Date, sep="_"), ".rds", sep=""), sep="_")))
ps_GC <- readRDS(file.path(path_Output_16S, paste("ps_GC", paste(paste("Filter_ASV_besttax_16S", Date, sep="_"), ".rds", sep=""), sep="_")))
ps_GCWF <- readRDS(file.path(path_Output_16S, paste("ps_GCWF", paste(paste("Filter_ASV_besttax_16S", Date, sep="_"), ".rds", sep=""), sep="_")))
ps_OEWF <- readRDS(file.path(path_Output_16S, paste("ps_OEWF", paste(paste("Filter_ASV_besttax_16S", Date, sep="_"), ".rds", sep=""), sep="_")))

pslist<- list("ps_SSU" = ps_SSU, "ps_WF" = ps_WF, "ps_Fish" = ps_Fish, "ps_OE" = ps_OE, "ps_GC" = ps_GC, "ps_OEWF" = ps_OEWF, "ps_GCWF" =ps_GCWF)

for (i in names(pslist)[grepl("ps", names(pslist))]){
  g <- paste(i)
  a <- length(pslist)
  ps <- pslist[[i]]
  ps_clr <- microbiome::transform(ps, "clr")
  pslist[[a+1]] <- ps_clr
  names(pslist)[[a+1]] <- paste("clr", sub("ps", "\\1", g), sep="")}

for (i in names(pslist)[grepl("clr", names(pslist))]){
  g <- paste(i)
  a <- length(pslist)
  clr <- pslist[[i]]
  TSE<-mia::makeTreeSummarizedExperimentFromPhyloseq(clr)
  pslist[[a+1]] <- TSE
  names(pslist)[[a+1]] <- paste("TSEc.l.r", sub("clr", "\\1", g), sep="")}
```

#-

# Save Data

```{r, message=FALSE, warning=FALSE}
###########
#Save Data#
###########
saveRDS(pslist, file.path(path_Output_16S, paste(paste(save_name, "ps_16S_merge_Filter_ASV_besttax", Date, sep="_"), ".rds", sep="")))

```

#-

# 13 Abiotics 

Visualization of abiotic measurements taken during the cruises or gathered from continuous monitoring in the Elbe estuary

## 13.1 Abiotics

```{r, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}

AbioticsFGG <- readRDS(file.path(path_Input_16S, "AbioticsFGG_16.02.24.rds"))
Mean_AbioticsFGG <- readRDS(file.path(path_Input_16S, "Mean_AbioticsFGG_16.02.24.rds"))

Abiotics_plot_list <- list()
Variables <-  c(
      "Salinity", "Temperature", "O2",
        "NH4",  "NO2", "NO3", 
        "PO4", "pH", "SPM", "TOC")
for (ii in Variables) {
      
      
      FILENAME    <- paste(paste(save_name, "Abiotics", ii, "Area_plot", sep="_"),".png", sep="")
    
      ggg     <- paste(ii) 

        
      p <- SAMDF16S %>%
        filter(!duplicated(paste(Season, LOC))) %>%
        ggplot(aes(x= fLOC, y=.data[[ii]])) + 
        geom_area(position = "identity", alpha = 0.2, size =1 , 
                  aes(colour = fSeason, group=fSeason, fill =fSeason)) + 
      scale_fill_manual(values = col.Palette$col.Palette.Season) +
      scale_color_manual(values = col.Palette$col.Palette.Season) + 
      theme(legend.position = "none") +
      theme(
         panel.background = element_rect(fill='transparent'),
         plot.background = element_rect(fill='transparent', color=NA),
         #panel.grid.major = element_blank(),
         #panel.grid.minor = element_blank(),
         legend.background = element_rect(fill='transparent'),
         legend.box.background = element_rect(fill='transparent') ) 
      
       if (ii %in% c("PO4", "pH", "SPM", "TOC")) {
          p <- p + theme(axis.text.x = element_text(angle = 90, size=15,face = "bold"),
          axis.title.x.bottom = element_blank(),
          axis.title.y.left = element_text(size=15,face = "bold"),
          strip.text.x = element_text(face = "bold"),
          strip.text.x.bottom = element_text(size = 15,face = "bold"),
          strip.text.y.left = element_text(size = 15,face = "bold"),
          axis.text.x.bottom = element_text(face = "bold", angle = 45, hjust = 1),
          axis.text.y.left = element_text(size = 15, face = "bold"),
          legend.title = element_text( size = 9),
          legend.text = element_text(size = 9,face = "bold"),
          axis.title.x=element_blank(),
          plot.subtitle = element_text(size = 9),
          plot.caption = element_text(size = 9))
       } else {
          p <- p + theme(axis.text.x = element_text(angle = 90, size=15,face = "bold"),
          axis.title.x.bottom = element_blank(),
          axis.title.y.left = element_text(size=15,face = "bold"),
          strip.text.x = element_text(face = "bold"),
          strip.text.x.bottom = element_text(size = 15,face = "bold"),
          strip.text.y.left = element_text(size = 15,face = "bold"),
          axis.text.x.bottom = element_blank(),
          axis.text.y.left = element_text(size = 15, face = "bold"),
          legend.title = element_text( size = 9),
          legend.text = element_text(size = 9,face = "bold"),
          axis.title.x=element_blank(),
          axis.ticks.x =element_blank(),
          plot.subtitle = element_text(size = 9),
          plot.caption = element_text(size = 9))
      }
      p <- p + labs(y = noquote(paste(ii, " [", noquote(Units[ii]), "]", sep = ""))) 

      Abiotics_plot<- cowplot::plot_grid(p, labels = c(""), ncol = 1)

      #Abiotics_plot <- cowplot::plot_grid(prow, ncol = 1, rel_heights = c(0.05, 0.98)) #title, 
      
      #plot(Abiotics_plot)
      ggsave(Abiotics_plot, filename = FILENAME, path = pathPlots, device='png', dpi=300, width = 4,
      height = 4)
      Abiotics_plot_list[[ii]] <- Abiotics_plot
  }

  ##############
  #Summary Plot#
  ##############
  PLOTS1 <- Abiotics_plot_list[!grepl("pH" , names(Abiotics_plot_list))]
  cowplot::plot_grid(cowplot::plot_grid(plotlist = PLOTS1, ncol = 3)) -> part_2_a #, labels = "auto"

  ggsave(part_2_a, filename = paste(paste("Abiotics_Facet",
          sep="_"),".png", sep=""), path = pathPlots , device='png', dpi=300, width = 8,height = 6)
  
  plot(part_2_a)

```




## 13.1 Timeseries Abiotics

```{r, message=FALSE, warning=FALSE, fig.width=10, fig.height=12}
### 1.1.6  Visualize Timeseries
library(cowplot)
ElbeAbiotics <- readRDS(file.path(path_Input_16S, "ElbeAbioticsDaily10.04.23.rds")) 


ElbeAbiotics$LOC<-ifelse(ElbeAbiotics$Loc == "Medem Grund", "MG-713",
                      ifelse(ElbeAbiotics$Loc == "Brunsbuettel", "BB-692",
                          ifelse(ElbeAbiotics$Loc == "Schwarztonnen Sand", "SS-665",
                                  ifelse(ElbeAbiotics$Loc == "Twielenfleth", "TF-651",
                                        ifelse(ElbeAbiotics$Loc == "Muehlenberger Loch", "ML-633", NA)))))
ElbeAbiotics$fLOC <- factor(ElbeAbiotics$LOC, levels=rev(LOCOrder))


ElbeAbiotics_filtered <- ElbeAbiotics %>%
  filter(Day >= "2021-05-01" & Day <= "2022-11-01")


# Create plots for each abiotic variable
colors_O2 <- c("red", "pink", "lightblue", "#3333FF", "#3333FF", "#3333FF")
breaks_O2 <- c(0,2,5, 7, 10, 14)
plot_O2 <- ggplot(ElbeAbiotics_filtered, aes(x = Day, y = fLOC, fill = O2)) +
  geom_tile() +
  scale_fill_gradientn(breaks = breaks_O2, colours = colors_O2) +
  theme_minimal() +
  labs(x = "", y = "") +
  scale_x_date(breaks = "month", date_labels = "%b-%Y") +
  ggtitle("Oxygen levels [mg/L]") +
   theme(
        axis.title.y.left = element_text(size=10,face = "bold"),
        strip.text.x = element_text(face = "bold"),
        strip.text.x.bottom = element_text(size = 10,face = "bold"),
        strip.text.y.left = element_text(size = 10,face = "bold"),
        axis.text.y.left = element_text(face = "bold"),
        legend.title = element_blank(),
        legend.text = element_text(size = 10,face = "bold"),
        plot.title = element_text(size = 10, face = "bold"),
        plot.subtitle = element_text(size = 9),
        plot.caption = element_text(size = 9), 
        axis.title.x = element_blank(),  # Remove x-axis title
        axis.text.x = element_blank()) 

colors_Temperature  <- c("blue","lightblue",  "red")
breaks_Temperature  <- c(0, 5, 15, 20, 25)
plot_Temperature <- ggplot(ElbeAbiotics_filtered, aes(x = Day, y = fLOC, fill = Temperature)) +
  geom_tile() +
  scale_fill_gradientn(breaks = breaks_Temperature, colours = colors_Temperature) +
  theme_minimal() + 
  labs(x = "", y = "") +
  scale_x_date(breaks = "month", date_labels = "%b-%Y") +
  ggtitle("Temperature [C°]") +
   theme(
        axis.title.y.left = element_text(size=10,face = "bold"),
        strip.text.x = element_text(face = "bold"),
        strip.text.x.bottom = element_text(size = 10,face = "bold"),
        strip.text.y.left = element_text(size = 10,face = "bold"),
        axis.text.y.left = element_text(face = "bold"),
        legend.title = element_blank(),
        legend.text = element_text(size = 10,face = "bold"),
        plot.title = element_text(size = 10, face = "bold"),
        plot.subtitle = element_text(size = 9),
        plot.caption = element_text(size = 9), 
        axis.title.x = element_blank(),  # Remove x-axis title
        axis.text.x = element_blank()) 


colors_Salinity  <- c("lightblue", "gold2", "gold")
breaks_Salinity  <- c(0, 0.5, 5, 20)
plot_Salinity <- ggplot(ElbeAbiotics_filtered, aes(x = Day, y = fLOC, fill = Salinity)) +
  geom_tile() +
  scale_fill_gradientn(breaks = breaks_Salinity , colours = colors_Salinity ) +
  theme_minimal() + 
  labs(x = "", y = "") +
  ggtitle("Salinity levels [psu]") +
  labs(x = NULL, y = NULL) +  # Remove x-axis label
  scale_x_date(breaks = "month", date_labels = "%b-%Y") +
  theme(
        axis.title.y.left = element_text(size=10,face = "bold"),
        strip.text.x = element_text(face = "bold"),
        strip.text.x.bottom = element_text(size = 10,face = "bold"),
        strip.text.y.left = element_text(size = 10,face = "bold"),
        axis.text.y.left = element_text(face = "bold"),
        legend.title = element_blank(),
        legend.text = element_text(size = 10,face = "bold"),
        plot.title = element_text(size = 10, face = "bold"),
        plot.subtitle = element_text(size = 9),
        plot.caption = element_text(size = 9), 
        axis.title.x = element_blank(),  # Remove x-axis title
        axis.text.x = element_blank()) 

colors_Turbidity  <- c("#FFFFFF", "#ac6721", "#663300")
breaks_Turbidity   <- c(0, 10, 50, 300)
plot_Turbidity <- ggplot(ElbeAbiotics_filtered, aes(x = Day, y = fLOC, fill = Turbidity)) +
  geom_tile() +
  scale_fill_gradientn(breaks = breaks_Turbidity  , colours = colors_Turbidity ) +
  theme_minimal() + 
  ggtitle("Turbidity levels [NTU]") +
  labs(x = NULL, y = NULL) +  # Remove x-axis label
  scale_x_date(breaks = "month", date_labels = "%b-%Y") +
  theme(axis.text.x = element_text(angle = 90),
        axis.title.x.bottom = element_text(size=10,face = "bold"),
        axis.title.y.left = element_text(size=10,face = "bold"),
        strip.text.x = element_text(face = "bold"),
        strip.text.x.bottom = element_text(size = 10,face = "bold"),
        strip.text.y.left = element_text(size = 10,face = "bold"),
        axis.text.x.bottom = element_text(face = "bold", angle = 45, hjust = 1),
        axis.text.y.left = element_text(face = "bold"),
        legend.title = element_blank(),
        legend.text = element_text(size = 10,face = "bold"),
        plot.title = element_text(size = 10, face = "bold"),
        plot.subtitle = element_text(size = 9),
        plot.caption = element_text(size = 9))



combined_plot <- plot_grid(plot_O2, plot_Temperature, plot_Salinity,plot_Turbidity,
                             labels = c("", ""), rel_heights = c(0.23, 0.23, 0.23, 0.28), ncol = 1, align = "v")
#combined_plot <- plot_grid(plot_O2, plot_Temperature, plot_Salinity,
#                             labels = c("", ""), rel_heights = c(0.28, 0.28, 0.32), ncol = 1, align = "v")
  plot(combined_plot)
  ggsave(combined_plot, filename = paste(paste(save_name,"ElbeAbioticsDaily", sep="_"), 
                                           ".png", sep=""), 
             path = pathPlots , device='png', dpi=300, width = 7, height = 5)

```

#-

# 14 Stable Isotopes

## 14.1 OE carbon 

```{r, message=FALSE, warning=FALSE, fig.width=6, fig.height=8}
library(readxl)
SIA <- as.data.frame(read_excel(file.path(path_Input_16S, "OE_SIA_19.06.2024.xlsx")))[,-1]
SIA[SIA$Stat == "TF",]$Stat <- paste("TW")
SIA[SIA$Stat == "STS",]$Stat <- paste("SS")
SIA$Number <- as.numeric(str_extract(SIA$Code, "\\d{1,2}$"))

#Rename Samples
SIA <- SIA %>%
  mutate(SampleID = paste0(
    "OE",
    case_when(
      Season == "Spring" ~ "SP",
      Season == "Summer" ~ "SU",
      Season == "Autumn" ~ "AU",
      Season == "Winter" ~ "WI",
      TRUE ~ NA_character_  # Fallback in case of unexpected season value
    ),
    substr(Year, 3, 4),  # Extract last two digits of the year
    paste(SIA$Stat),
    case_when(
      Tide == "Ebb" ~ "EB",
      Tide == "Flood" ~ "FL",
      TRUE ~ NA_character_  # Fallback in case of unexpected tide value
    ),
    SIA$Number # Extract last character of the Code column
  ))


SIA <- SIA[SIA$SampleID %in% SAMDF16S$SampleID, ]
SIA <- SAMDF16S %>%
  left_join(SIA[c("SampleID", "Code", "TL_cm", "Weight_g", "Group", "Class", "Strategy", "%C","%N","C/N","d15N","d13C")])
SIA_OE <- SIA[SIA$Species == "OE",]
SIA_OE$d13C <- as.numeric(SIA_OE$d13C)



  Datasetname <- "OE"
  FILENAME    <- paste(paste(save_name, "SIA_BarPlot", Datasetname, sep="_"), ".png", sep="")      
    
  COL <- col.Palette$col.Palette.Reps[names(col.Palette$col.Palette.Reps) %in%   
                                        unique(SIA_OE$Reps)]
      
   SIA_OE$Reps <-  factor( SIA_OE$Reps, levels = RepOrder[RepOrder %in%  SIA_OE$Reps])

      Short.labs <- gsub("[^0-9]", "", SIA_OE$Reps)
      names(Short.labs) <- SIA_OE$Reps
      
      
      p <- ggplot(SIA_OE, aes(x = SampleID, y = d13C, color = d13C, fill = d13C)) + 
          geom_point(size = 5) +  # Increase point size
           ylim(- 27, -13) +
          #geom_bar(stat = "identity") +
          #geom_area(fill = "lightblue", alpha = 0.5) +
          coord_flip() +
          facet_grid(rows = vars(Reps), drop = TRUE, scale = "free", space = "free_y", switch = "y", 
             labeller = labeller(Reps = Short.labs)) +
            scale_color_gradientn(colors = c("#F8766D", "#9E9E9E", "steelblue")) 

      p <- p + 
        ylab(expression(paste(delta^{13}, "C (\u2030)"))) + xlab("") + 
        labs(fill="") + #atheme+
        #scale_fill_manual(values = color_mapping) +
        #ylim(0, 80) +
            theme(axis.title.y=element_blank(),
            axis.text.y=element_blank(),
            axis.ticks.y=element_blank()) +
        theme(
         panel.background = element_rect(fill='transparent'), #transparent panel bg
         plot.background = element_rect(fill='transparent', color=NA), #transparent plot bg
         ) +
      theme(axis.title.x.bottom =  element_text(color="grey13", size=15, face ="bold"), 
        strip.text = element_text(color = "black", face= "bold")) +
      theme(
        legend.title=element_text(size=9), 
        legend.text=element_text(size=9), 
        axis.text.x.bottom = element_text(size= 15, face = "bold", angle = 45, hjust = 1),
        #strip.text.y.left = element_text(size = 9,face = "bold"), 
        #axis.title.y.left = element_text(size=12,face = "bold")
        ) +
        theme(legend.position = "none")
      p <- p +
        geom_hline(yintercept= - 25.6,linetype=1) +
        geom_hline(yintercept= - 26.5,linetype=2) +
        geom_hline(yintercept= - 20.2,linetype=1) +
        geom_hline(yintercept= - 19.6,linetype=2)

      g <- ggplot_gtable(ggplot_build(p))
        stripr <- which(grepl('strip-l', g$layout$name))
        fills <- alpha(COL, 0.8)
        k <- 1
        for (iii in stripr) {
        j <- which(grepl('rect', g$grobs[[iii]]$grobs[[1]]$childrenOrder))
        g$grobs[[iii]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
        k <- k+1}
        
    SIA_BarPlot <- cowplot::plot_grid(g, labels = c(""), ncol = 1)
    SIA_BarPlot <- plot_grid(SIA_BarPlot, ncol = 1, rel_heights = c(100))
    ggsave(SIA_BarPlot, filename = FILENAME, path = pathPlots, device='png', dpi=300, width = 2.7, height = 10)
    
    plot(SIA_BarPlot)
```

## 14.2 GC carbon

```{r, message=FALSE, warning=FALSE, fig.width=6, fig.height=8}

library(readxl)
SIA <- as.data.frame(read_excel(file.path(path_Input_16S, "GC_SIA_19.06.2024.xlsx")))[,-1]
SIA[SIA$Stat == "TF",]$Stat <- paste("TW")
SIA[SIA$Stat == "STS",]$Stat <- paste("SS")
SIA$Number <- as.numeric(str_extract(SIA$Code2, "\\d{1,2}$"))

#Rename Samples
SIA <- SIA %>%
  mutate(SampleID = paste0(
    "GC",
    case_when(
      Season == "Spring" ~ "SP",
      Season == "Summer" ~ "SU",
      Season == "Autumn" ~ "AU",
      Season == "Winter" ~ "WI",
      TRUE ~ NA_character_  # Fallback in case of unexpected season value
    ),
    substr(Year, 3, 4),  # Extract last two digits of the year
    paste(SIA$Stat),
    case_when(
      Tide == "Ebb" ~ "EB",
      Tide == "Flood" ~ "FL",
      TRUE ~ NA_character_  # Fallback in case of unexpected tide value
    ),
    SIA$Number # Extract last character of the Code column
  ))


SIA <- SIA[SIA$SampleID %in% SAMDF16S$SampleID, ]
SIA <- SAMDF16S %>%
  left_join(SIA[c("SampleID", "Code", "TL_cm", "Weight_g", "Group", "Class", "Strategy", "%C","%N","C/N","d15N","d13C")])
SIA_GC <- SIA[SIA$Species == "GC",]
SIA_GC$d13C <- as.numeric(SIA_GC$d13C)



  Datasetname <- "GC"
  FILENAME    <- paste(paste(save_name, "SIA_BarPlot", Datasetname, sep="_"), ".png", sep="")      
    
  COL <- col.Palette$col.Palette.Reps[names(col.Palette$col.Palette.Reps) %in%   
                                        unique(SIA_GC$Reps)]
      
   SIA_GC$Reps <-  factor( SIA_GC$Reps, levels = RepOrder[RepOrder %in%  SIA_GC$Reps])

      Short.labs <- gsub("[^0-9]", "", SIA_GC$Reps)
      names(Short.labs) <- SIA_GC$Reps
      
      
      p <- ggplot(SIA_GC, aes(x = SampleID, y = d13C, color = d13C, fill = d13C)) + 
          geom_point(size = 5) +  # Increase point size
           ylim(- 27, -13) +
          #geom_bar(stat = "identity") +
          #geom_area(fill = "lightblue", alpha = 0.5) +
          coord_flip() +
          facet_grid(rows = vars(Reps), drop = TRUE, scale = "free", space = "free_y", switch = "y", 
             labeller = labeller(Reps = Short.labs)) +
            scale_color_gradientn(colors = c("#F8766D", "#9E9E9E")) 

      p <- p + 
        ylab(expression(paste(delta^{13}, "C (\u2030)"))) + xlab("") + 
        labs(fill="") + #atheme+
        #scale_fill_manual(values = color_mapping) +
        #ylim(0, 80) +
            theme(axis.title.y=element_blank(),
            axis.text.y=element_blank(),
            axis.ticks.y=element_blank()) +
        theme(
         panel.background = element_rect(fill='transparent'), #transparent panel bg
         plot.background = element_rect(fill='transparent', color=NA), #transparent plot bg
         ) +
      theme(axis.title.x.bottom =  element_text(color="grey13", size=15, face ="bold"), 
        strip.text = element_text(color = "black", face= "bold")) +
      theme(
        legend.title=element_text(size=9), 
        legend.text=element_text(size=9), 
        axis.text.x.bottom = element_text(size= 15, face = "bold", angle = 45, hjust = 1),
        #strip.text.y.left = element_text(size = 9,face = "bold"), 
        #axis.title.y.left = element_text(size=12,face = "bold")
        ) +
        theme(legend.position = "none")
      p <- p +
        geom_hline(yintercept= - 25.6,linetype=1) +
        geom_hline(yintercept= - 26.5,linetype=2) +
        geom_hline(yintercept= - 20.2,linetype=1) +
        geom_hline(yintercept= - 19.6,linetype=2)

      g <- ggplot_gtable(ggplot_build(p))
        stripr <- which(grepl('strip-l', g$layout$name))
        fills <- alpha(COL, 0.8)
        k <- 1
        for (iii in stripr) {
        j <- which(grepl('rect', g$grobs[[iii]]$grobs[[1]]$childrenOrder))
        g$grobs[[iii]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
        k <- k+1}
        
    SIA_BarPlot <- cowplot::plot_grid(g, labels = c(""), ncol = 1)
    SIA_BarPlot <- plot_grid(SIA_BarPlot, ncol = 1, rel_heights = c(100))
    ggsave(SIA_BarPlot, filename = FILENAME, path = pathPlots, device='png', dpi=300, width = 2.7, height = 10)
    
    plot(SIA_BarPlot)
    
```


